---
title: "Coding Exercise 7_Question"
---

## **Coding Exercise 7 - Parsing Dates**

### **Question 1: How much time has passed?**

When doing Data Science projects, we might come accross data in Date format that refers to a certain point in time. They often come in very different formats - some may only have the date, some may have the month and year, and some even has the exact time (hours, minutes, seconds) and timezone.

Clue: You can use any libraries to help you.

In this exercise, explore some ways how to load a string that tells us date so we can calculate the difference between the two input dates.

You will be tasked to write a function called `duration_count` which takes in 2 inputs. Both of the inputs are string that tells you the date. The output of your function should be the duration between the 2 inputs, in seconds.

The input format will be: "Date Month Year Hour:Minute:Second Timezone_Information"

#### **Example 1:**

-   Input 1 = 'Mon 23 Jan 2017 14:41:10 -0800'

-   Input 2 = 'Mon 23 Jan 2017 14:41:10 -0200'

Both inputs refer to the same date and same time, but in different timezones. Therefore, the duration between these two dates are: 6 hours. But, as we want the answer to be in seconds, the expected answer is 21600 seconds. (Just output 21600, you don't have to write seconds).

#### **Example 2:**

-   Input 1 = 'Mon 23 Dec 2017 14:00:00 -0700'

-   Input 2 = 'Tue 24 Dec 2017 14:00:00 -0700'

Both inputs refer to the same time and are located in the same time zone. However, they are 1 day apart. Therefore, the duration between them are: 1 day = 1 x 24 x 3600 = 86400 seconds.

```{r}
library(tidyverse)
library(lubridate)
library(tidyr)
duration_count <- function(input_1, input_2) {
  df <- data.frame(matrix(ncol = 1, nrow = 2))
  x <- c("data")
  colnames(df) <- x
  df[1,1] <- input_1
  df[2,1] <- input_2
  df <- separate(df, col = data, into = c("day","date","month","year","time","timezone"), sep = " ")
  df <- separate(df, col = time, into = c("hour","min","sec"), sep = ":")
  df <- df %>% mutate(date = as.numeric(date),
                      year = as.numeric(year),
                      hour = as.numeric(hour),
                      min = as.numeric(min),
                      sec = as.numeric(sec),
                      timezone = as.numeric(timezone))
  df <- df[order(-df$date),]
  gap_day = df$date[1] - df$date[2]
  gap_hour = df$hour[1] - df$hour[2]
  gap_min = df$min[1] - df$min[2]
  gap_sec = df$sec[1] - df$sec[2]
  gap_zone = df$timezone[1] - df$timezone[2]
  Total_duration = (gap_day * 24 * 3600) + (gap_hour * 3600) + (gap_min * 60) + gap_sec - ((gap_zone/100) * 3600)
  Total_duration
}
duration_count(input_1 = 'Mon 23 Jan 2017 14:41:10 -0800', input_2 = 'Mon 23 Jan 2017 14:41:10 -0200')
```
```{r}

duration_count(input_1 = "Mon 23 Dec 2017 14:00:00 -0700",input_2 = "Tue 24 Dec 2017 14:00:00 -0700")

```

### **Question 2: What Day is It?**

In time series data, we usually want to know what day is it. It usually isn't enough to just know the 'number' of date, especially when days matter a lot to our data (example: customer behavior analysis). In a customer behavior analysis scenario, we might find different behaviors in Monday - Friday vs Saturday - Sunday (weekend). Knowing the days also allow us to map some seasonality.

Given 3 input: date first, then month, and finally year. Can you tell us what day is it? You can use any library that you want. Your function name should be named `find_day`.

#### **Example 1:**

`find_day(11,10,2021)` should give output "Monday", as 11 October 2021 is a Monday.

#### **Example 2:**

`find_day(17,8,1945)` should give output "Friday", as 17 August 1945 is a Friday.

```{r}
find_day <- function(day, month, year){
  df <- data.frame(matrix(nrow = 1, ncol = 3))
  x <- c("year","month","day")
  colnames(df) <- x
  df[1,1] <- year
  df[1,2] <- month
  df[1,3] <- day
  df <- df %>% 
    mutate(date_ = paste(year,month,day))
  df$ndate <- as.Date(df$date_, format = "%Y%m%d")
  df$day_ <- weekdays(df$ndate)
  df$day_[1]
}

find_day(11,10,2021)

```
```{r}

find_day(17,8,1945)

```
